### 2021-01-11 ch03_esmvaltool/esmvaltool.tex
Cleaned tex files and added text to chapter 4

In order to answer the research questions of this thesis posed in
\cref{sec:01:research_questions}, a reliable and efficient tool to read,
process and evaluate climate model output and observational data is necessary.
A valuable software that fits these criteria is the \ac{ESMValTool}. The
\ac{ESMValTool} is an open-source community diagnostics and performance metrics
tool for the routine evaluation of \ac{ESM} output, which notably facilitates
the analysis of \ac{CMIP} models (\url{https://www.esmvaltool.org}). For this
reason, all analyses presented in
\cref{ch:04:assessment_climate_metrics,ch:05:paper_ecs,ch:06:paper_gpp} of this
thesis were implemented into the \ac{ESMValTool}. Apart from that, further
substantial changes and additions to the code base of the \ac{ESMValTool} have
been contributed that improve the routine evaluation of climate models, which
is beneficial for the entire scientific community. This lead to co-authorship
in the scientific documentation of the \ac{ESMValTool}, which is published in
four peer-reviewed studies \autocite{Eyring2020, Lauer2020, Righi2020,
  Weigel2020}. After a brief overview over the \ac{ESMValTool}'s structure,
this chapter presents all these contributions that are not documented in other
chapters of this thesis.

@@

As of December 2020, 40408 lines of code have been added and 21050 lines of
code have been removed from to the GitHub repository of \ac{ESMValCore} by the
author of this thesis. Apart from general improvements of the code base, these
changes and additions mainly include new preprocessor functions that can be
applied to the input data and derivation scripts for new non-\ac{CMOR}
variables. \Cref{tab:03:changes_to_esmvalcore} shows a summary of these main
contributions, which are partly published in the scientific documentation of
\ac{ESMValCore} \autocite{Righi2020}.

@@

In addition to the analyses presented in
\cref{ch:04:assessment_climate_metrics,ch:05:paper_ecs,ch:06:paper_gpp},
several more recipes and \ac{CMOR}ization scripts for observational data have
been added to the main \ac{ESMValTool} repository on GitHub. Moreover, multiple
minor changes and additions have been implemented to improve the code base
and/or to fix bugs. In total, the author of this study has added 88668 lines of
code and removed 47816 lines of code from the \ac{ESMValTool} repository (as of
December 2020). Parts of these implementations are already published in the
scientific documentation of the \ac{ESMValTool}, which covers large-scale
diagnostics \autocite{Eyring2020}, diagnostics for emergent constraints and
future projections \autocite{Lauer2020} and diagnostics for extreme events and
regional evaluation \autocite{Weigel2020}.

@@

Due to an exhaustive overhaul of the \ac{ESMValTool} version 2, older recipes
from version 1 \autocite{Eyring2016a} cannot be used directly in the latest
release. Porting recipes from the old version to the current version requires
substantial changes on the recipes themselves, but also on the corresponding
diagnostic scripts. As of December 2020, the author of this thesis has ported
two recipes originally written by other authors to the new version of
\ac{ESMValTool}: \emph{recipe\_anav13jclim.yml} and
\emph{recipe\_wenzel16jclim.yml}. \emph{recipe\_anav13jclim.yml} reproduces the
analysis of \textcite{Anav2013}, who evaluate carbon cycle-related variables
for \acp{ESM} of the \acs{CMIP}5 ensemble. This includes climatologies, trends
and variabilities of important quantities of the terrestrial and oceanic carbon
cycle like carbon fluxes, carbon reservoir sizes and vegetation distributions.
\emph{recipe\_wenzel16jclim.yml} includes the \ac{MDER} analysis performed by
\textcite{Wenzel2016a} to constrain future changes in the position of the
austral jet stream. Due to its flexible code, the corresponding diagnostic
scripts can be used to apply the \ac{MDER} method to arbitrary target variables
and predictors.

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other chapters of this thesis, namely
\emph{recipe\_bock20jgr.yml} (\cref{ch:04:assessment_climate_metrics}),
\emph{recipe\_schlund20esd.yml} (\cref{ch:05:paper_ecs}) and
\emph{recipe\_schlund20jgr\_*.yml} (\cref{ch:06:paper_gpp}).
\emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml} contain diagnostic scripts
that are able to calculate the climate metrics \ac{ECS} and \ac{TCR} for
arbitrary model output (see \cref{sec:02:climate_sensitivity}). Corresponding
plots are shown in \cref{fig:02:gregory_regression,fig:02:tcr}.
\emph{recipe\_cox18nature.yml} reproduces the analysis of \textcite{Cox2018},
who introduce an emergent constraint in \ac{ECS} based on a global temperature
variability metric $\Psi$. \Cref{fig:03:cox18:a} shows $\Psi$ over the past 85
years for \acs{CMIP}5 models and observations form HadCRUT4
\autocite{Morice2012}. Since high sensitivity climate models exhibit higher
values of $\Psi$ than low sensitivity models, an emergent relationship between
\ac{ECS} and $\Psi$ can be established (\cref{fig:03:cox18:b}). With
observations of $\Psi$, \ac{ECS} can eventually be constrained to $\left( 2.8
\pm 0.6 \right) \unit{K}$ ($66 \unit{\%}$ confidence range). More details on
this including the calculation of $\Psi$ are given in \cref{subsec:05:cox}.

>>>>

In order to answer the research questions of this thesis posed in
\cref{sec:01:research_questions}, a reliable and efficient tool to read,
process and evaluate climate model output and observational data is necessary.
A valuable software that fits these criteria is the \ac{ESMValTool}. The
\ac{ESMValTool} is an open-source community diagnostics and performance metrics
tool for the routine evaluation of \ac{ESM} output, which notably facilitates
the analysis of \ac{CMIP} models (\url{https://www.esmvaltool.org}). For this
reason, all analyses presented in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs,ch:06:paper_gpp} of this
thesis were implemented into the \ac{ESMValTool}. Apart from that, further
substantial changes and additions to the code base of the \ac{ESMValTool} have
been contributed that improve the routine evaluation of climate models, which
is beneficial for the entire scientific community. This lead to co-authorship
in the scientific documentation of the \ac{ESMValTool}, which is published in
four peer-reviewed studies \autocite{Eyring2020, Lauer2020, Righi2020,
  Weigel2020}. After a brief overview over the \ac{ESMValTool}'s structure,
this chapter presents all these contributions that are not documented in other
chapters of this thesis.

@@

As of \TheMonth{}, 40408 lines of code have been added and 21050 lines of code
have been removed from to the GitHub repository of \ac{ESMValCore} by the
author of this thesis. Apart from general improvements of the code base, these
changes and additions mainly include new preprocessor functions that can be
applied to the input data and derivation scripts for new non-\ac{CMOR}
variables. \Cref{tab:03:changes_to_esmvalcore} shows a summary of these main
contributions, which are partly published in the scientific documentation of
\ac{ESMValCore} \autocite{Righi2020}.

@@

In addition to the analyses presented in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs,ch:06:paper_gpp}, several
more recipes and \ac{CMOR}ization scripts for observational data have been
added to the main \ac{ESMValTool} repository on GitHub. Moreover, multiple
minor changes and additions have been implemented to improve the code base
and/or to fix bugs. In total, the author of this study has added 88668 lines of
code and removed 47816 lines of code from the \ac{ESMValTool} repository (as of
\TheMonth{}). Parts of these implementations are already published in the
scientific documentation of the \ac{ESMValTool}, which covers large-scale
diagnostics \autocite{Eyring2020}, diagnostics for emergent constraints and
future projections \autocite{Lauer2020} and diagnostics for extreme events and
regional evaluation \autocite{Weigel2020}.

@@

Due to an exhaustive overhaul of the \ac{ESMValTool} version 2, older recipes
from version 1 \autocite{Eyring2016a} cannot be used directly in the latest
release. Porting recipes from the old version to the current version requires
substantial changes on the recipes themselves, but also on the corresponding
diagnostic scripts. As of \TheMonth{}, the author of this thesis has ported two
recipes originally written by other authors to the new version of
\ac{ESMValTool}: \emph{recipe\_anav13jclim.yml} and
\emph{recipe\_wenzel16jclim.yml}. \emph{recipe\_anav13jclim.yml} reproduces the
analysis of \textcite{Anav2013}, who evaluate carbon cycle-related variables
for \acp{ESM} of the \acs{CMIP}5 ensemble. This includes climatologies, trends
and variabilities of important quantities of the terrestrial and oceanic carbon
cycle like carbon fluxes, carbon reservoir sizes and vegetation distributions.
\emph{recipe\_wenzel16jclim.yml} includes the \ac{MDER} analysis performed by
\textcite{Wenzel2016a} to constrain future changes in the position of the
austral jet stream. Due to its flexible code, the corresponding diagnostic
scripts can be used to apply the \ac{MDER} method to arbitrary target variables
and predictors.

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other chapters of this thesis, namely
\emph{recipe\_bock20jgr.yml} (\cref{ch:04:papers_ecs_tcr_assessment}),
\emph{recipe\_schlund20esd.yml} (\cref{ch:05:paper_ecs}) and
\emph{recipe\_schlund20jgr\_*.yml} (\cref{ch:06:paper_gpp}).
\emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml} contain diagnostic scripts
that are able to calculate the climate metrics \ac{ECS} and \ac{TCR} for
arbitrary model output (see \cref{sec:02:climate_sensitivity}). Corresponding
plots are shown in \cref{fig:02:gregory_regression,fig:02:tcr}.
\emph{recipe\_cox18nature.yml} reproduces the analysis of \textcite{Cox2018},
who introduce an emergent constraint in \ac{ECS} based on a global temperature
variability metric $\Psi$. \Cref{fig:03:cox18:a} shows $\Psi$ over the past 85
years for \acs{CMIP}5 models and observations form HadCRUT4
\autocite{Morice2012}. Since high sensitivity climate models exhibit higher
values of $\Psi$ than low sensitivity models, an emergent relationship between
\ac{ECS} and $\Psi$ can be established (\cref{fig:03:cox18:b}). With
observations of $\Psi$, \ac{ECS} can eventually be constrained to $\left( 2.8
\pm 0.6 \right) \unit{K}$ ($66 \unit{\%}$ confidence range). More details on
this including the calculation of $\Psi$ are given in \cref{subsec:05:cox}.

### 2021-01-11 ch05_paper_ecs/paper_ecs.tex
Initialized chapters
Added first figure
Added further text and figures to ch.2
Added section 2.2
Added section on emergent constraints
Added figures for ESMValTool contributions (chapter 3)
Finished chapter 3
Cleaned tex files and added text to chapter 4

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                        Assessment of climate metrics                        %
%=============================================================================%

\chapter{Assessment of Climate Metrics in CMIP6}
\label{ch:assessment_climate_metrics}

@@

>>>>

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                                  Paper ECS                                  %
%=============================================================================%

\chapter{Evaluation of Emergent Constraints on the \acl{ECS} in \acs{CMIP}6}
\label{ch:05:paper_ecs}

@@

\section{Comparison of Emergent Constraints on \acs{ECS} for \acs{CMIP}5 and \acs{CMIP}6}
\label{sec:05:comparison_of_emergent_constraints}

\subsection{COX}
\label{subsec:05:cox}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Sed arcu non odio euismod. Quis
risus sed vulputate odio ut. Quis commodo odio aenean sed adipiscing diam donec
adipiscing tristique. Habitant morbi tristique senectus et. Eleifend donec
pretium vulputate sapien nec sagittis aliquam malesuada bibendum. Lobortis
feugiat vivamus at augue. Sit amet commodo nulla facilisi nullam. Viverra vitae
congue eu consequat ac felis donec. Tortor dignissim convallis aenean et tortor
at risus. Condimentum id venenatis a condimentum. Orci phasellus egestas tellus
rutrum tellus pellentesque eu tincidunt tortor. Neque volutpat ac tincidunt
vitae semper quis. Etiam erat velit scelerisque in dictum non consectetur a.
Pellentesque adipiscing commodo elit at imperdiet dui accumsan sit. Senectus et
netus et malesuada. Eget gravida cum sociis natoque penatibus et. Purus ut
faucibus pulvinar elementum. Nulla facilisi etiam dignissim diam quis enim
lobortis scelerisque fermentum.

Non diam phasellus vestibulum lorem sed risus. Vitae suscipit tellus mauris a
diam maecenas sed enim. Sed odio morbi quis commodo odio aenean sed adipiscing
diam. Mauris pharetra et ultrices neque ornare aenean euismod. Diam quis enim
lobortis scelerisque. Nisi vitae suscipit tellus mauris a diam. Et netus et
malesuada fames. Urna neque viverra justo nec ultrices dui. Maecenas accumsan
lacus vel facilisis volutpat est velit egestas dui. Eget magna fermentum
iaculis eu non diam phasellus vestibulum lorem. Volutpat consequat mauris nunc
congue nisi vitae suscipit tellus.

Ac tortor dignissim convallis aenean et tortor at risus. Consequat mauris nunc
congue nisi vitae. Gravida neque convallis a cras semper auctor. Faucibus
turpis in eu mi bibendum neque. Lorem mollis aliquam ut porttitor leo a diam.
Facilisis gravida neque convallis a cras semper auctor neque vitae. Nunc
aliquet bibendum enim facilisis gravida neque convallis a cras. Bibendum enim
facilisis gravida neque convallis a cras semper auctor. Ut enim blandit
volutpat maecenas volutpat blandit. Quis ipsum suspendisse ultrices gravida
dictum fusce ut. Dictumst quisque sagittis purus sit amet volutpat consequat
mauris nunc. Non arcu risus quis varius quam quisque id diam vel.

Pellentesque sit amet porttitor eget. Enim nulla aliquet porttitor lacus. Enim
eu turpis egestas pretium aenean pharetra magna ac placerat. In vitae turpis
massa sed elementum tempus. Cras semper auctor neque vitae tempus quam
pellentesque nec nam. Sollicitudin tempor id eu nisl. Nunc aliquet bibendum
enim facilisis gravida neque. Imperdiet sed euismod nisi porta. Est ullamcorper
eget nulla facilisi etiam dignissim diam quis. Cursus mattis molestie a iaculis
at erat pellentesque adipiscing commodo. Elit sed vulputate mi sit amet mauris
commodo quis. Quis risus sed vulputate odio. Orci a scelerisque purus semper
eget. Scelerisque eu ultrices vitae auctor. Cum sociis natoque penatibus et
magnis dis parturient. Id aliquet risus feugiat in ante metus. Pretium quam
vulputate dignissim suspendisse in.

Velit aliquet sagittis id consectetur purus ut faucibus pulvinar. Venenatis a
condimentum vitae sapien pellentesque habitant morbi tristique. Ut etiam sit
amet nisl purus in mollis. Etiam dignissim diam quis enim. Id leo in vitae
turpis. Et magnis dis parturient montes nascetur ridiculus. Gravida rutrum
quisque non tellus orci. Eu consequat ac felis donec et. Egestas purus viverra
accumsan in nisl nisi scelerisque eu. Elit ullamcorper dignissim cras tincidunt
lobortis feugiat vivamus at. Maecenas pharetra convallis posuere morbi leo urna
molestie. Nunc id cursus metus aliquam eleifend mi. Mauris ultrices eros in
cursus turpis massa. Lectus nulla at volutpat diam.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Sed arcu non odio euismod. Quis
risus sed vulputate odio ut. Quis commodo odio aenean sed adipiscing diam donec
adipiscing tristique. Habitant morbi tristique senectus et. Eleifend donec
pretium vulputate sapien nec sagittis aliquam malesuada bibendum. Lobortis
feugiat vivamus at augue. Sit amet commodo nulla facilisi nullam. Viverra vitae
congue eu consequat ac felis donec. Tortor dignissim convallis aenean et tortor
at risus. Condimentum id venenatis a condimentum. Orci phasellus egestas tellus
rutrum tellus pellentesque eu tincidunt tortor. Neque volutpat ac tincidunt
vitae semper quis. Etiam erat velit scelerisque in dictum non consectetur a.
Pellentesque adipiscing commodo elit at imperdiet dui accumsan sit. Senectus et
netus et malesuada. Eget gravida cum sociis natoque penatibus et. Purus ut
faucibus pulvinar elementum. Nulla facilisi etiam dignissim diam quis enim
lobortis scelerisque fermentum.

Non diam phasellus vestibulum lorem sed risus. Vitae suscipit tellus mauris a
diam maecenas sed enim. Sed odio morbi quis commodo odio aenean sed adipiscing
diam. Mauris pharetra et ultrices neque ornare aenean euismod. Diam quis enim
lobortis scelerisque. Nisi vitae suscipit tellus mauris a diam. Et netus et
malesuada fames. Urna neque viverra justo nec ultrices dui. Maecenas accumsan
lacus vel facilisis volutpat est velit egestas dui. Eget magna fermentum
iaculis eu non diam phasellus vestibulum lorem. Volutpat consequat mauris nunc
congue nisi vitae suscipit tellus.

Ac tortor dignissim convallis aenean et tortor at risus. Consequat mauris nunc
congue nisi vitae. Gravida neque convallis a cras semper auctor. Faucibus
turpis in eu mi bibendum neque. Lorem mollis aliquam ut porttitor leo a diam.
Facilisis gravida neque convallis a cras semper auctor neque vitae. Nunc
aliquet bibendum enim facilisis gravida neque convallis a cras. Bibendum enim
facilisis gravida neque convallis a cras semper auctor. Ut enim blandit
volutpat maecenas volutpat blandit. Quis ipsum suspendisse ultrices gravida
dictum fusce ut. Dictumst quisque sagittis purus sit amet volutpat consequat
mauris nunc. Non arcu risus quis varius quam quisque id diam vel.

Pellentesque sit amet porttitor eget. Enim nulla aliquet porttitor lacus. Enim
eu turpis egestas pretium aenean pharetra magna ac placerat. In vitae turpis
massa sed elementum tempus. Cras semper auctor neque vitae tempus quam
pellentesque nec nam. Sollicitudin tempor id eu nisl. Nunc aliquet bibendum
enim facilisis gravida neque. Imperdiet sed euismod nisi porta. Est ullamcorper
eget nulla facilisi etiam dignissim diam quis. Cursus mattis molestie a iaculis
at erat pellentesque adipiscing commodo. Elit sed vulputate mi sit amet mauris
commodo quis. Quis risus sed vulputate odio. Orci a scelerisque purus semper
eget. Scelerisque eu ultrices vitae auctor. Cum sociis natoque penatibus et
magnis dis parturient. Id aliquet risus feugiat in ante metus. Pretium quam
vulputate dignissim suspendisse in.

Velit aliquet sagittis id consectetur purus ut faucibus pulvinar. Venenatis a
condimentum vitae sapien pellentesque habitant morbi tristique. Ut etiam sit
amet nisl purus in mollis. Etiam dignissim diam quis enim. Id leo in vitae
turpis. Et magnis dis parturient montes nascetur ridiculus. Gravida rutrum
quisque non tellus orci. Eu consequat ac felis donec et. Egestas purus viverra
accumsan in nisl nisi scelerisque eu. Elit ullamcorper dignissim cras tincidunt
lobortis feugiat vivamus at. Maecenas pharetra convallis posuere morbi leo urna
molestie. Nunc id cursus metus aliquam eleifend mi. Mauris ultrices eros in
cursus turpis massa. Lectus nulla at volutpat diam.

### 2021-01-11 ch06_paper_gpp/paper_gpp.tex
Initialized chapters
Added first figure
Added further text and figures to ch.2
Added overview of climate feedbacks
Added section on emergent constraints
Added figures for ESMValTool contributions (chapter 3)
Cleaned tex files and added text to chapter 4

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                                  Paper ECS                                  %
%=============================================================================%

\chapter{Evaluation of Emergent Constraints on ECS in CMIP6}
\label{ch:paper_ecs}

@@

>>>>

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                                  Paper GPP                                  %
%=============================================================================%

\chapter{Constraining Future \acl{GPP} with Machine Learning}
\label{ch:06:paper_gpp}

@@

\section{Step 1: XXXXXXXXXXXXXXXXXX}
\label{sec:06:step_1}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Sed arcu non odio euismod. Quis
risus sed vulputate odio ut. Quis commodo odio aenean sed adipiscing diam donec
adipiscing tristique. Habitant morbi tristique senectus et. Eleifend donec
pretium vulputate sapien nec sagittis aliquam malesuada bibendum. Lobortis
feugiat vivamus at augue. Sit amet commodo nulla facilisi nullam. Viverra vitae
congue eu consequat ac felis donec. Tortor dignissim convallis aenean et tortor
at risus. Condimentum id venenatis a condimentum. Orci phasellus egestas tellus
rutrum tellus pellentesque eu tincidunt tortor. Neque volutpat ac tincidunt
vitae semper quis. Etiam erat velit scelerisque in dictum non consectetur a.
Pellentesque adipiscing commodo elit at imperdiet dui accumsan sit. Senectus et
netus et malesuada. Eget gravida cum sociis natoque penatibus et. Purus ut
faucibus pulvinar elementum. Nulla facilisi etiam dignissim diam quis enim
lobortis scelerisque fermentum.

Non diam phasellus vestibulum lorem sed risus. Vitae suscipit tellus mauris a
diam maecenas sed enim. Sed odio morbi quis commodo odio aenean sed adipiscing
diam. Mauris pharetra et ultrices neque ornare aenean euismod. Diam quis enim
lobortis scelerisque. Nisi vitae suscipit tellus mauris a diam. Et netus et
malesuada fames. Urna neque viverra justo nec ultrices dui. Maecenas accumsan
lacus vel facilisis volutpat est velit egestas dui. Eget magna fermentum
iaculis eu non diam phasellus vestibulum lorem. Volutpat consequat mauris nunc
congue nisi vitae suscipit tellus.

Ac tortor dignissim convallis aenean et tortor at risus. Consequat mauris nunc
congue nisi vitae. Gravida neque convallis a cras semper auctor. Faucibus
turpis in eu mi bibendum neque. Lorem mollis aliquam ut porttitor leo a diam.
Facilisis gravida neque convallis a cras semper auctor neque vitae. Nunc
aliquet bibendum enim facilisis gravida neque convallis a cras. Bibendum enim
facilisis gravida neque convallis a cras semper auctor. Ut enim blandit
volutpat maecenas volutpat blandit. Quis ipsum suspendisse ultrices gravida
dictum fusce ut. Dictumst quisque sagittis purus sit amet volutpat consequat
mauris nunc. Non arcu risus quis varius quam quisque id diam vel.

Pellentesque sit amet porttitor eget. Enim nulla aliquet porttitor lacus. Enim
eu turpis egestas pretium aenean pharetra magna ac placerat. In vitae turpis
massa sed elementum tempus. Cras semper auctor neque vitae tempus quam
pellentesque nec nam. Sollicitudin tempor id eu nisl. Nunc aliquet bibendum
enim facilisis gravida neque. Imperdiet sed euismod nisi porta. Est ullamcorper
eget nulla facilisi etiam dignissim diam quis. Cursus mattis molestie a iaculis
at erat pellentesque adipiscing commodo. Elit sed vulputate mi sit amet mauris
commodo quis. Quis risus sed vulputate odio. Orci a scelerisque purus semper
eget. Scelerisque eu ultrices vitae auctor. Cum sociis natoque penatibus et
magnis dis parturient. Id aliquet risus feugiat in ante metus. Pretium quam
vulputate dignissim suspendisse in.

Velit aliquet sagittis id consectetur purus ut faucibus pulvinar. Venenatis a
condimentum vitae sapien pellentesque habitant morbi tristique. Ut etiam sit
amet nisl purus in mollis. Etiam dignissim diam quis enim. Id leo in vitae
turpis. Et magnis dis parturient montes nascetur ridiculus. Gravida rutrum
quisque non tellus orci. Eu consequat ac felis donec et. Egestas purus viverra
accumsan in nisl nisi scelerisque eu. Elit ullamcorper dignissim cras tincidunt
lobortis feugiat vivamus at. Maecenas pharetra convallis posuere morbi leo urna
molestie. Nunc id cursus metus aliquam eleifend mi. Mauris ultrices eros in
cursus turpis massa. Lectus nulla at volutpat diam.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor
incididunt ut labore et dolore magna aliqua. Sed arcu non odio euismod. Quis
risus sed vulputate odio ut. Quis commodo odio aenean sed adipiscing diam donec
adipiscing tristique. Habitant morbi tristique senectus et. Eleifend donec
pretium vulputate sapien nec sagittis aliquam malesuada bibendum. Lobortis
feugiat vivamus at augue. Sit amet commodo nulla facilisi nullam. Viverra vitae
congue eu consequat ac felis donec. Tortor dignissim convallis aenean et tortor
at risus. Condimentum id venenatis a condimentum. Orci phasellus egestas tellus
rutrum tellus pellentesque eu tincidunt tortor. Neque volutpat ac tincidunt
vitae semper quis. Etiam erat velit scelerisque in dictum non consectetur a.
Pellentesque adipiscing commodo elit at imperdiet dui accumsan sit. Senectus et
netus et malesuada. Eget gravida cum sociis natoque penatibus et. Purus ut
faucibus pulvinar elementum. Nulla facilisi etiam dignissim diam quis enim
lobortis scelerisque fermentum.

Non diam phasellus vestibulum lorem sed risus. Vitae suscipit tellus mauris a
diam maecenas sed enim. Sed odio morbi quis commodo odio aenean sed adipiscing
diam. Mauris pharetra et ultrices neque ornare aenean euismod. Diam quis enim
lobortis scelerisque. Nisi vitae suscipit tellus mauris a diam. Et netus et
malesuada fames. Urna neque viverra justo nec ultrices dui. Maecenas accumsan
lacus vel facilisis volutpat est velit egestas dui. Eget magna fermentum
iaculis eu non diam phasellus vestibulum lorem. Volutpat consequat mauris nunc
congue nisi vitae suscipit tellus.

Ac tortor dignissim convallis aenean et tortor at risus. Consequat mauris nunc
congue nisi vitae. Gravida neque convallis a cras semper auctor. Faucibus
turpis in eu mi bibendum neque. Lorem mollis aliquam ut porttitor leo a diam.
Facilisis gravida neque convallis a cras semper auctor neque vitae. Nunc
aliquet bibendum enim facilisis gravida neque convallis a cras. Bibendum enim
facilisis gravida neque convallis a cras semper auctor. Ut enim blandit
volutpat maecenas volutpat blandit. Quis ipsum suspendisse ultrices gravida
dictum fusce ut. Dictumst quisque sagittis purus sit amet volutpat consequat
mauris nunc. Non arcu risus quis varius quam quisque id diam vel.

Pellentesque sit amet porttitor eget. Enim nulla aliquet porttitor lacus. Enim
eu turpis egestas pretium aenean pharetra magna ac placerat. In vitae turpis
massa sed elementum tempus. Cras semper auctor neque vitae tempus quam
pellentesque nec nam. Sollicitudin tempor id eu nisl. Nunc aliquet bibendum
enim facilisis gravida neque. Imperdiet sed euismod nisi porta. Est ullamcorper
eget nulla facilisi etiam dignissim diam quis. Cursus mattis molestie a iaculis
at erat pellentesque adipiscing commodo. Elit sed vulputate mi sit amet mauris
commodo quis. Quis risus sed vulputate odio. Orci a scelerisque purus semper
eget. Scelerisque eu ultrices vitae auctor. Cum sociis natoque penatibus et
magnis dis parturient. Id aliquet risus feugiat in ante metus. Pretium quam
vulputate dignissim suspendisse in.

Velit aliquet sagittis id consectetur purus ut faucibus pulvinar. Venenatis a
condimentum vitae sapien pellentesque habitant morbi tristique. Ut etiam sit
amet nisl purus in mollis. Etiam dignissim diam quis enim. Id leo in vitae
turpis. Et magnis dis parturient montes nascetur ridiculus. Gravida rutrum
quisque non tellus orci. Eu consequat ac felis donec et. Egestas purus viverra
accumsan in nisl nisi scelerisque eu. Elit ullamcorper dignissim cras tincidunt
lobortis feugiat vivamus at. Maecenas pharetra convallis posuere morbi leo urna
molestie. Nunc id cursus metus aliquam eleifend mi. Mauris ultrices eros in
cursus turpis massa. Lectus nulla at volutpat diam.
